\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-02-06 analysis/manuscript.Rmd
re compile

This study combines data from multiple publicly available data sources as visualised in Figure 1. 
Transformative agreement data retrieved from the cOAlition S Journal Checker Tool provided information about journal portfolios and participating institutions. 
After identification of hybrid journals, Crossref served as the primary data source for article-level metadata including Creative Commons (CC) license information to determine open access articles on publisher websites.
OpenAlex provided first author affiliation metadata that were subsequently linked to the transformative agreement data to identify open access articles published through these agreements. 
In total, the compiled data set consists of `r hoaddata::jn_ind |> filter(!cr_year %in% c("2017", "2023")) |> distinct(issn_l, cr_year, jn_all) |> pull(jn_all) |> sum()` articles published in `r hoaddata::jn_ind |> filter(!cr_year %in% c("2017", "2023")) |> distinct(issn_l) |> nrow()` hybrid journals between 2018 and 2022.

@@

Data gathering started with obtaining journals included in transformative agreements using the cOAlition S’ Journal Checker Tool publicly available Transformative Agreement Data dump.[^tadump] 
The dump consisted of multiple online Google spreadsheets where each data file represented one agreement listed in the ESAC Transformative Agreement Registry.[^esacregistry] 
Each file comprised information about journals and institutions involved per agreement. 
Because the Journal Checker Tool only only provides data about active transformative agreements, removing data representing expired transformative agreements, four different snapshots were used for this analysis: self-archived version from July 2021, July 2022, and May 2023, as well as the most current dump downloaded on 11 December 2023. 
This ensured that transformative agreements, which ended in 2021, were included in the analysis.
Agreements ending before 2021 could not be obtained.
Overall, the combined Transformative Agreement Data dumps contained `r  length(unique(hoaddata::jct_hybrid_jns$esac_id))` out of `r length(unique(esac_df$ID))` agreements listed in the ESAC registry by December 2023.

The Transformative Agreement Data dumps linked agreements to journals represented by journal names and ISSN. 
After mapping ISSN variants to the corresponding linking ISSN (ISSN-L) as provided by The ISSN International Centre, journals were associated to publishers using the ESAC ID, a unique identifier for transformative agreements in the ESAC Transformative Agreement Registry.
Because transformative agreements can include both full open access and hybrid journals, journal data were complemented with information about a journal's open access status using multiple sources: the Directory of Open Access Journals (DOAJ) downloaded on 12 December 2023[^doaj], OpenAlex (November 2023) and the the Bielefeld list of GOLD OA journals [@goldoa]. 
In total, `r n_oa_journals` full open access journals were excluded based on journal title matching.
Figure shows an overlap between the three data sources of
`r round(length(unique(Reduce(intersect, my_venn))) / length(unique(Reduce(union, my_venn)))* 100,0)`%.
However, combining different data sources considerably extended the journal matching to exclude full open access journals from transformative agreements.
The Gold OA journals dataset alone adds `r length(unique(Reduce(setdiff, my_venn)))` journals, while the DOAJ comprised `r length(setdiff(my_venn$DOAJ, union(my_venn[["GOLD OA"]], my_venn$OpenAlex)))` full open access journals not listed in either of the other two sources. 
These full open access journals were mostly launched in 2022.

@@

After identifying hybrid journals included in transformative agreements, article metadata was retrieved from Crossref and mapped to OpenAlex to obtain affiliation metadata. 
The Crossref November 2023 database snapshot was used to determine the journals’ yearly publication volume for the 5-year period 2018 to 2022. 
Because Crossref metadata did not distinguish between research articles and other types of journal content, only included articles published in regular issues indicated by non-numeric pagination were included.
Furthermore, an expanded version of Unpaywall’s paratext recognition approach was applied to exclude non-scholarly journal content such as table of contents.

Open access articles in hybrid journals were identified through Creative Commons (CC) license information in Crossref metadata and mapped them to the different CC variants. 
License information relative to the "accepted manuscript (AM)" version were not considered. 
Crossref was used for open access identification because transformative agreements generally require publishers to deposit CC license information.
Comparing Crossref license coverage with OpenAlex, which re-uses open access evidence from Unpaywall, a widely used open access discovery service, revealed a slight discrepancy between these two data sources.
Overall, `r hoaddata::cr_upw |> filter(cr_year %in% 2018:2022, cat == "Global", issn_l != "0027-8424") |> distinct(issn_l, cr_year, cr_hybrid_total) |> pull(cr_hybrid_total) |> sum()` articles with CC license were retrieved using Crossref, while `r hoaddata::cr_upw |> filter(cr_year %in% 2018:2022, cat == "Global", issn_l != "0027-8424") |> distinct(issn_l, cr_year, upw_hybrid_total) |> pull(upw_hybrid_total) |> sum()` articles were tagged as "hybrid" in OpenAlex. 
The biggest differences concerned articles published between 2018 and 2020, and among some publishers that presumably did not provide CC license information to Crossref including AIP Publishing, American Physiological Society and Emerald.
Crossref license metadata was more complete with regard to articles from the publisher Wiley.
During the data collection, inconsistent open access status information in previous OpenAlex version was observed [@jahn2023], which might explain this discrepancy.

Next, the number and proportion of open access articles per journal was calculated. 
To improve the identification of hybrid journals, journals with an open access proportion above 95% were excluded.
This further step allowed to remove additional `r length(unique(oa_prop$issn_l))` full open access journals.

Affiliation data is a crucial data point for the planning and evaluation of transformative agreements [@Schimmer_2015; @Geschuhn_2017]. 
Author affiliations were retrieved from OpenAlex.
Generally, corresponding authors are responsible to arrange open access publication [@Borrego_2020].
However, because of low coverage, this study focuses on first author and their affiliations.
First authors typically contribute most to a paper and are often considered lead author research papers [@Larivi_re_2016]. 
Overall, around 90% of studied articles had first author affiliation metadata in OpenAlex, whereas the coverage of articles with corresponding author information was around 54%.

@@

In total, the compiled data set consists of `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l, cr_year, jn_all) |> pull(jn_all) |> sum()` articles published in `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l) |> nrow()` hybrid journals between 2018 and 2022. 
They represented around

@@

>>>>

This study combines data from multiple publicly available data sources as visualised in Figure 1. 
Transformative agreement data retrieved from the cOAlition S Journal Checker Tool provided information about journal portfolios and participating institutions. 
After identification of hybrid journals, Crossref served as the primary data source for article-level metadata including Creative Commons (CC) license information to determine open access articles on publisher websites.
OpenAlex provided first author affiliation metadata that were subsequently linked to the transformative agreement data to identify open access articles published through these agreements.

@@

Data gathering started with obtaining journals included in transformative agreements using the publicly available Transformative Agreement Data dump[^tadump] used by the cOAlition S Journal Checker Tool.[^checkertool] 
The dump consisted of multiple online Google spreadsheets where each data file represented one agreement listed in the ESAC Transformative Agreement Registry.[^esacregistry] 
Each file comprised information about journals and institutions involved per agreement. 
Because the Journal Checker Tool only provided data about active transformative agreements, data representing expired transformative agreements were constantly removed. Therefore, four different snapshots were used for this analysis: self-archived version from July 2021, July 2022, and May 2023, as well as the most current dump downloaded on 11 December 2023. 
This ensured that transformative agreements, which ended in 2021, were included in the analysis.
Agreements ending before 2021 could not be obtained.
Overall, the combined Transformative Agreement Data dumps contained `r  length(unique(hoaddata::jct_hybrid_jns$esac_id))` out of `r length(unique(esac_df$ID))` agreements listed in the ESAC registry by December 2023.

The Transformative Agreement Data dumps link agreements to journals represented by journal names and ISSN. 
After mapping ISSN variants to the corresponding linking ISSN (ISSN-L) as provided by The ISSN International Centre, journals were associated to publishers using the ESAC ID, a unique identifier for transformative agreements in the ESAC Transformative Agreement Registry.
Because transformative agreements can include both full open access and hybrid journals, the data were complemented with information about a journal's open access status using multiple sources: the Directory of Open Access Journals (DOAJ) downloaded on 12 December 2023[^doaj], OpenAlex (November 2023) and the the Bielefeld list of GOLD OA journals [@goldoa]. 
In total, `r n_oa_journals` full open access journals were excluded based on ISSN matching.
Figure shows an overlap between the three data sources of
`r round(length(unique(Reduce(intersect, my_venn))) / length(unique(Reduce(union, my_venn)))* 100,0)`%.
However, combining different data sources considerably extended the journal matching to exclude full open access journals from transformative agreements.
The Gold OA journals dataset alone adds `r length(unique(Reduce(setdiff, my_venn)))` journals, while the DOAJ comprised `r length(setdiff(my_venn$DOAJ, union(my_venn[["GOLD OA"]], my_venn$OpenAlex)))` full open access journals not listed in either of the other two sources. 
These full open access journals were mostly launched in 2022.

@@

After identifying hybrid journals included in transformative agreements, article metadata was retrieved from Crossref and mapped to OpenAlex for obtaining author metadata including affiliations. 
The Crossref November 2023 database snapshot was used to determine the journals’ yearly publication volume for the five-year period 2018 to 2022. 
Because Crossref metadata lacked information to distinguish between research articles and other types of journal content, only articles published in regular issues indicated by non-numeric pagination were included.
Furthermore, an expanded version of Unpaywall’s paratext recognition approach was applied to exclude non-scholarly journal content such as table of contents.

Open access articles in hybrid journals were identified through Creative Commons (CC) license information in Crossref metadata. 
License information relative to the "accepted manuscript (AM)" version were not considered. 
Crossref was used for open access identification because transformative agreements generally require publishers to deposit CC license information.
Comparing Crossref license coverage with OpenAlex, which re-uses open access evidence from Unpaywall, a widely used open access discovery service, revealed a slight discrepancy between these two data sources.
Overall, `r hoaddata::cr_upw |> filter(cr_year %in% 2018:2022, cat == "Global", issn_l != "0027-8424") |> distinct(issn_l, cr_year, cr_hybrid_total) |> pull(cr_hybrid_total) |> sum()` articles with CC license were retrieved using Crossref, while `r hoaddata::cr_upw |> filter(cr_year %in% 2018:2022, cat == "Global", issn_l != "0027-8424") |> distinct(issn_l, cr_year, upw_hybrid_total) |> pull(upw_hybrid_total) |> sum()` articles were tagged as "hybrid" in OpenAlex. 
The biggest differences concerned articles published between 2018 and 2020.
In 2022, however, Crossref and OpenAlex open access numbers only differ slightly (`r hoaddata::cr_upw |> filter(cr_year %in% 2022, cat == "Global", issn_l != "0027-8424") |> distinct(issn_l, cr_year, cr_hybrid_total) |> pull(cr_hybrid_total) |> sum()` records using Crossref vs. `r hoaddata::cr_upw |> filter(cr_year %in% 2022, cat == "Global", issn_l != "0027-8424") |> distinct(issn_l, cr_year, upw_hybrid_total) |> pull(upw_hybrid_total) |> sum()` in OpenAlex).
Upon inspection, notable difference could be furthermore observed among some publishers that presumably did not provide CC license information to Crossref including AIP Publishing, American Physiological Society and Emerald.
Crossref license metadata was more complete with regard to articles from the publisher Wiley and American Chemical Society.
<!-- During the data collection, inconsistent open access status information in previous OpenAlex versions was observed [@jahn2023], which might explain this discrepancy.-->

After retrieving article metadata, the publication volume including open access was calculated per journal. 
To improve the identification of hybrid journals, journals with an open access proportion above 95% were excluded.
This further step allowed to remove additional `r length(unique(oa_prop$issn_l))` full open access journals.

Author metadata are crucial for the planning and evaluation of transformative agreements [@Schimmer_2015; @Geschuhn_2017], in particular information about corresponding authors who are generally responsible to arrange open access publication [@Borrego_2020]. 
Author affiliations were retrieved from OpenAlex.
However, because of low coverage, this study focused on first authors and their affiliations.
First authors typically contribute most to a paper and are often considered lead author research papers [@Larivi_re_2016]. 
Overall, around 90% of studied articles had first author affiliation metadata in OpenAlex, whereas the coverage of articles with corresponding author information was around 54%.

@@

To assess the impact of transformative agreements to hybrid open access, eligible institutions per agreement as listed in the Transformative Agreement Data dump. 
According to the documentation, data about participating institutions were crowd-sourced from the agreements and consortia that successfully negotiated an agreement.
Eligible were automatically matched to first author affiliations recorded by OpenAlex using the ROR-ID.
The matching also took into account the duration of an agreement according to the ESAC registry.
Upon inspection, Transformative Agreement Data did not cover  associated institutions comprehensively like university hospitals or institutes of large research organisations like the Max Planck Society. 
To improve the matching, Transformative Agreement Data was automatically enriched with associated institutions.

In total, the compiled data set consists of `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l, cr_year, jn_all) |> pull(jn_all) |> sum()` articles published in `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l) |> nrow()` hybrid journals between 2018 and 2022. 
Hybrid journals included in transformative agreements represented `r cr_stats |> filter(src == "hoad") |> pull(n_articles) |> sum() / cr_stats |> pull(n_articles) |> sum() * 100`%  of total global output over the same time period according to Crossref, while full open access journals

@@

[^checkertool]: <https://www.coalition-s.org/blog/enabling-accurate-results-within-the-journal-checker-tool/>

### 2024-02-06 analysis/manuscript.tex
re compile

This study combines data from multiple publicly available data sources
as visualised in Figure 1. Transformative agreement data retrieved from
the cOAlition S Journal Checker Tool provided information about journal
portfolios and participating institutions. After identification of
hybrid journals, Crossref served as the primary data source for
article-level metadata including Creative Commons (CC) license
information to determine open access articles on publisher websites.
OpenAlex provided first author affiliation metadata that were
subsequently linked to the transformative agreement data to identify
open access articles published through these agreements. In total, the
compiled data set consists of 8,942,669 articles published in 12,858
hybrid journals between 2018 and 2022.

@@

Data gathering started with obtaining journals included in
transformative agreements using the cOAlition S' Journal Checker Tool
publicly available Transformative Agreement Data dump.\footnote{\url{https://journalcheckertool.org/transformative-agreements/}}
The dump consisted of multiple online Google spreadsheets where each
data file represented one agreement listed in the ESAC Transformative
Agreement Registry.\footnote{\url{https://esac-initiative.org/about/transformative-agreements/agreement-registry/}}
Each file comprised information about journals and institutions involved
per agreement. Because the Journal Checker Tool only only provides data
about active transformative agreements, removing data representing
expired transformative agreements, four different snapshots were used
for this analysis: self-archived version from July 2021, July 2022, and
May 2023, as well as the most current dump downloaded on 11 December
2023. This ensured that transformative agreements, which ended in 2021,
were included in the analysis. Agreements ending before 2021 could not
be obtained. Overall, the combined Transformative Agreement Data dumps
contained 729 out of 869 agreements listed in the ESAC registry by
December 2023.

The Transformative Agreement Data dumps linked agreements to journals
represented by journal names and ISSN. After mapping ISSN variants to
the corresponding linking ISSN (ISSN-L) as provided by The ISSN
International Centre, journals were associated to publishers using the
ESAC ID, a unique identifier for transformative agreements in the ESAC
Transformative Agreement Registry. Because transformative agreements can
include both full open access and hybrid journals, journal data were
complemented with information about a journal's open access status using
multiple sources: the Directory of Open Access Journals (DOAJ)
downloaded on 12 December 2023\footnote{\url{https://doaj.org/csv}},
OpenAlex (November 2023) and the the Bielefeld list of GOLD OA journals
(Bruns et al., 2022). In total, 3,439 full open access journals were
excluded based on journal title matching. Figure shows an overlap
between the three data sources of 72\%. However, combining different
data sources considerably extended the journal matching to exclude full
open access journals from transformative agreements. The Gold OA
journals dataset alone adds 176 journals, while the DOAJ comprised 10
full open access journals not listed in either of the other two sources.
These full open access journals were mostly launched in 2022.

@@

After identifying hybrid journals included in transformative agreements,
article metadata was retrieved from Crossref and mapped to OpenAlex to
obtain affiliation metadata. The Crossref November 2023 database
snapshot was used to determine the journals' yearly publication volume
for the 5-year period 2018 to 2022. Because Crossref metadata did not
distinguish between research articles and other types of journal
content, only included articles published in regular issues indicated by
non-numeric pagination were included. Furthermore, an expanded version
of Unpaywall's paratext recognition approach was applied to exclude
non-scholarly journal content such as table of contents.

Open access articles in hybrid journals were identified through Creative
Commons (CC) license information in Crossref metadata and mapped them to
the different CC variants. License information relative to the
``accepted manuscript (AM)'' version were not considered. Crossref was
used for open access identification because transformative agreement
standards require publishers to deposit CC license information.
Comparing Crossref license coverage with OpenAlex, which re-uses open
access evidence from Unpaywall, a widely used open access discovery
service, revealed a slight discrepancy between these two data sources.
Overall, 847,107 articles with CC license were retrieved using Crossref,
while 1,055,765 articles were tagged as ``hybrid'' in OpenAlex. The
biggest differences concerned articles published between 2018 and 2020,
and among some publishers that presumably did not provide CC license
information to Crossref including AIP Publishing, American Physiological
Society and Emerald (\textbf{ludo?}). Crossref license metadata was more
complete with regard to articles from the publisher Wiley. During the
data collection, inconsistent open access status information in previous
OpenAlex version was observed (Jahn et al., 2023), which might explain
this discrepancy.

Next, the number and proportion of open access articles per journal was
calculated. To improve the identification of hybrid journals, journals
with an open access proportion above 95\% were excluded. This further
step allowed to remove additional 241 full open access journals.

Affiliation data is a crucial data point for the planning and evaluation
of transformative agreements (Geschuhn \& Stone, 2017; Schimmer et al.,
2015). Author affiliations were retrieved from OpenAlex. Generally,
corresponding authors are responsible to arrange open access publication
(Borrego et al., 2020). However, because of low coverage, this study
focuses on first author and their affiliations. First authors typically
contribute most to a paper and are often considered lead author research
papers (Larivière et al., 2016). Overall, around 90\% of studied
articles had first author affiliation metadata in OpenAlex, whereas the
coverage of articles with corresponding author information was around
54\%.

In total, the compiled data set consists of 8,922,146 articles published
in 12,857 hybrid journals between 2018 and 2022. They represented around

@@

\leavevmode\vadjust pre{\hypertarget{ref-jahn2023}{}}%
Jahn, N., Haupka, N., \& Hobert, A. (2023). \emph{Analysing and
reclassifying open access information in OpenAlex}. Blog post.
\url{https://subugoe.github.io/scholcomm_analytics/posts/oalex_oa_status/}

>>>>

This study combines data from multiple publicly available data sources
as visualised in Figure 1. Transformative agreement data retrieved from
the cOAlition S Journal Checker Tool provided information about journal
portfolios and participating institutions. After identification of
hybrid journals, Crossref served as the primary data source for
article-level metadata including Creative Commons (CC) license
information to determine open access articles on publisher websites.
OpenAlex provided first author affiliation metadata that were
subsequently linked to the transformative agreement data to identify
open access articles published through these agreements.

@@

Data gathering started with obtaining journals included in
transformative agreements using the publicly available Transformative
Agreement Data dump\footnote{\url{https://journalcheckertool.org/transformative-agreements/}}
used by the cOAlition S Journal Checker Tool.\footnote{\url{https://www.coalition-s.org/blog/enabling-accurate-results-within-the-journal-checker-tool/}}
The dump consisted of multiple online Google spreadsheets where each
data file represented one agreement listed in the ESAC Transformative
Agreement Registry.\footnote{\url{https://esac-initiative.org/about/transformative-agreements/agreement-registry/}}
Each file comprised information about journals and institutions involved
per agreement. Because the Journal Checker Tool only provided data about
active transformative agreements, data representing expired
transformative agreements were constantly removed. Therefore, four
different snapshots were used for this analysis: self-archived version
from July 2021, July 2022, and May 2023, as well as the most current
dump downloaded on 11 December 2023. This ensured that transformative
agreements, which ended in 2021, were included in the analysis.
Agreements ending before 2021 could not be obtained. Overall, the
combined Transformative Agreement Data dumps contained 729 out of 869
agreements listed in the ESAC registry by December 2023.

The Transformative Agreement Data dumps link agreements to journals
represented by journal names and ISSN. After mapping ISSN variants to
the corresponding linking ISSN (ISSN-L) as provided by The ISSN
International Centre, journals were associated to publishers using the
ESAC ID, a unique identifier for transformative agreements in the ESAC
Transformative Agreement Registry. Because transformative agreements can
include both full open access and hybrid journals, the data were
complemented with information about a journal's open access status using
multiple sources: the Directory of Open Access Journals (DOAJ)
downloaded on 12 December 2023\footnote{\url{https://doaj.org/csv}},
OpenAlex (November 2023) and the the Bielefeld list of GOLD OA journals
(Bruns et al., 2022). In total, 3,439 full open access journals were
excluded based on ISSN matching. Figure shows an overlap between the
three data sources of 72\%. However, combining different data sources
considerably extended the journal matching to exclude full open access
journals from transformative agreements. The Gold OA journals dataset
alone adds 176 journals, while the DOAJ comprised 10 full open access
journals not listed in either of the other two sources. These full open
access journals were mostly launched in 2022.

@@

After identifying hybrid journals included in transformative agreements,
article metadata was retrieved from Crossref and mapped to OpenAlex for
obtaining author metadata including affiliations. The Crossref November
2023 database snapshot was used to determine the journals' yearly
publication volume for the five-year period 2018 to 2022. Because
Crossref metadata lacked information to distinguish between research
articles and other types of journal content, only articles published in
regular issues indicated by non-numeric pagination were included.
Furthermore, an expanded version of Unpaywall's paratext recognition
approach was applied to exclude non-scholarly journal content such as
table of contents.

Open access articles in hybrid journals were identified through Creative
Commons (CC) license information in Crossref metadata. License
information relative to the ``accepted manuscript (AM)'' version were
not considered. Crossref was used for open access identification because
transformative agreements generally require publishers to deposit CC
license information. Comparing Crossref license coverage with OpenAlex,
which re-uses open access evidence from Unpaywall, a widely used open
access discovery service, revealed a slight discrepancy between these
two data sources. Overall, 742,369 articles with CC license were
retrieved using Crossref, while 950,260 articles were tagged as
``hybrid'' in OpenAlex. The biggest differences concerned articles
published between 2018 and 2020. In 2022, however, Crossref and OpenAlex
open access numbers only differ slightly (249,511 records using Crossref
vs.~255,344 in OpenAlex). Upon inspection, notable difference could be
furthermore observed among some publishers that presumably did not
provide CC license information to Crossref including AIP Publishing,
American Physiological Society and Emerald. Crossref license metadata
was more complete with regard to articles from the publisher Wiley and
American Chemical Society.

After retrieving article metadata, the publication volume including open
access was calculated per journal. To improve the identification of
hybrid journals, journals with an open access proportion above 95\% were
excluded. This further step allowed to remove additional 241 full open
access journals.

Author metadata are crucial for the planning and evaluation of
transformative agreements (Geschuhn \& Stone, 2017; Schimmer et al.,
2015), in particular information about corresponding authors who are
generally responsible to arrange open access publication (Borrego et
al., 2020). Author affiliations were retrieved from OpenAlex. However,
because of low coverage, this study focused on first authors and their
affiliations. First authors typically contribute most to a paper and are
often considered lead author research papers (Larivière et al., 2016).
Overall, around 90\% of studied articles had first author affiliation
metadata in OpenAlex, whereas the coverage of articles with
corresponding author information was around 54\%.

To assess the impact of transformative agreements to hybrid open access,
eligible institutions per agreement as listed in the Transformative
Agreement Data dump. According to the documentation, data about
participating institutions were crowd-sourced from the agreements and
consortia that successfully negotiated an agreement. Eligible were
automatically matched to first author affiliations recorded by OpenAlex
using the ROR-ID. The matching also took into account the duration of an
agreement according to the ESAC registry. Upon inspection,
Transformative Agreement Data did not cover associated institutions
comprehensively like university hospitals or institutes of large
research organisations like the Max Planck Society. To improve the
matching, Transformative Agreement Data was automatically enriched with
associated institutions.

In total, the compiled data set consists of 8,922,146 articles published
in 12,857 hybrid journals between 2018 and 2022. Hybrid journals
included in transformative agreements represented 40\% of total global
output over the same time period according to Crossref, while full open
access journals

@@
